---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mortgage

<!-- badges: start -->
<!-- badges: end -->

The goal of mortgage is to help understand the true cost of a mortgage. It also can help you easily compare between different mortgages. It is based on the [Python library of the same name](https://mortgage.readthedocs.io/en/latest/). The package is built using [R6](https://r6.r-lib.org/).

## Installation

You can install the development version of mortgage from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("parmsam/mortgage")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mortgage)
# Example usage  
loan <- Loan$new(principal=200000, interest=.06, term=30)
loan
```

```{r}
loan$summarize()
```


```{r}
loan$amortize()
```
## Compare loan objects

```{r}
# Create some Loan objects
loan1 <- Loan$new(principal = 100000, interest = 0.05, term = 30, term_unit = "years", compounded = "monthly")
loan2 <- Loan$new(principal = 150000, interest = 0.04, term = 15, term_unit = "years", compounded = "monthly")
loan3 <- Loan$new(principal = 200000, interest = 0.045, term = 20, term_unit = "years", compounded = "monthly")
# Create a LoanComparison object
loan_comparison <- LoanComparison$new(loans = list(loan1, loan2, loan3))
loan_comparison
```

```{r}
# Compare total interest
total_interest_comparison <- loan_comparison$compare_total_interest()
print(total_interest_comparison)
# Compare monthly payments
monthly_payments_comparison <- loan_comparison$compare_monthly_payments()
print(monthly_payments_comparison)
# Compare total payments
total_payments_comparison <- loan_comparison$compare_total_payments()
print(total_payments_comparison)
```

```{r}
# Print a summary of the loan comparison
loan_comparison$summarize()
```
